\documentclass[a4paper,12pt]{report}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}

\title{WASML: Nd-array, Classification and Regression}
\author{
  Bhonsle, Archit\\
  \and
  Patil, Ved\\
  \and
  Bhonsle, Gat\\
}

\begin{document}

\maketitle
\tableofcontents

\begin{abstract}
  In today’s day and age, machine learning has become increasingly an
  integral part of our businesses and lives. However, the current machine
  learning landscape is dominated by Python and its ML ecosystem consisting
  of Numpy, Pandas, Matplotlib and Sklearn. The most common way we
  interface with machine learning is through our browsers. Every time
  Facebook correctly tags someone in the photos we upload, or how YouTube
  decides to recommend us videos a machine learning model is running behind
  the scenes to make those predictions. The traditional way to do this is
  to use a server that takes in all the data and produces the output and
  sends it back. For complex models, this makes a lot of sense but for
  simple predictions, it is quite a bit of overhead when the calculation
  can be done on the device itself. The problem with using python for this
  is that they need a python runtime on the system which is not available
  on browsers. The aim of this project is to build a machine learning
  library that runs in the browser powered by WebAssembly. This paper will
  focus on building of the nd-array implementation and classification and
  regression models.
\end{abstract}

\end{document}
